% From: http://nitens.org/taraborelli/cvtex
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{verbatim,placeins}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=9in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}
\usepackage{hanging}
\usepackage[none]{hyphenat}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=0.7]{Monaco}

% CUSTOM COMMANDS
\newcommand{\amper}{{\fontspec[Scale=.95]{Linux Libertine O}\selectfont}}
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}

\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\footnotesize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Matt Jibson - vita},pdfauthor={Matt Jibson}]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

\begin{document}
\sloppy

\reversemarginpar
{{\huge Matt Jibson}\\[1.0cm]
\parbox{.5\linewidth}{
\vspace{\baselineskip}
303-902-6948\\
\href{mailto:matt.jibson@gmail.com}{matt.jibson@gmail.com}\\
}
\parbox{.5\linewidth}{
\begin{flushright}
\href{https://mattjibson.com/}{https://mattjibson.com/}\\
\href{https://github.com/mjibson}{https://github.com/mjibson}\\
\end{flushright}
}

\section*{Work Experience}

\years{July 2015-\\present}\textbf{CoreOS}\\Developer. \emph{go, python, kubernetes, docker}\\Features and maintenance for Quay.io.\\[.2cm]
\years{March 2012-\\July 2015}\textbf{Stack Overflow}\\Developer. \emph{go, c\#, javascript, sql-server, angularjs}\\Features and maintenance for Stack Overflow Careers. Internal applications for the SRE team. Primary author of Bosun, a Go-based monitoring and alerting system.\\[.2cm]
\years{June 2011-\\March 2012}\textbf{Seagate Technology}\\Senior Engineer. \emph{python, mysql}\\Wrote and maintained various custom tools and web apps to address or discover internal issues and problems.\\[.2cm]
\years{2000-2015}\textbf{US Geological Survey}\\Consultant. \emph{java, sql}\\Worked with a scientist to implement algorithms in usable programs. Various implementations written in C++, Java, PHP, SQL.\\[.2cm]

\section*{Software Development}

\href{https://github.com/bosun-monitor/bosun}{Bosun}\\Alerting and monitoring system in Go. Includes a cross-platform agent for autodetecting and collecting data.\\[.2cm]
\href{https://github.com/mjibson/mog}{mog}\\Audio player in Go that can play various kinds of music (wav, mp3, flac, vorbis, nintendo sound files) from different sources (google drive, dropbox, soundcloud, bandcamp, shoutcast, local machine) and works the same on popular OSs (Linux, Mac, Windows).\\[.2cm]
\href{https://github.com/mjibson/goread}{goread}\\Open-source RSS reader in Go, on App Engine with AngularJS. Profitable, with hundreds of paying users.\\[.2cm]
\href{https://github.com/mjibson/appstats}{appstats}\\Appstats for Go on Google App Engine. Ported from python.\\[.2cm]
\href{https://github.com/miniprofiler/go}{MiniProfiler}\\A simple but effective mini-profiler for Go websites.\\[.2cm]
\href{https://github.com/mjibson/goon}{goon}\\Autocaching interface to the App Engine datastore for Go.\\[.2cm]
\href{https://github.com/mjibson/nsf}{nsf}\\Nintendo Sound Format emulator for Go. Involves emulating a 6502 CPU, 2A03 audio chip, and a 65k RAM with register for the two chips to communicate.\\[.2cm]
\href{https://github.com/mjibson/go-dsp}{go-dsp}\\Digital Signal Processing package for the Go language. Contains functionality for the fast Fourier Transform and other useful functions.\\[.2cm]
\href{https://github.com/mjibson/slammer}{SLAMMER}\\Programs for seismic landslide analysis in Java.\\[.2cm]

\section*{Education}

\noindent\years{2009}\textbf{M.S., Electrical Engineering}\\
\emph{Colorado State University, 3.2 GPA.} TA for EE451 - Digital System Design and EE571 - VLSI System Design.\\[.2cm]
\years{2007}\textbf{B.S., Computer Engineering}\\
\emph{Colorado State University, 3.3 GPA.} Second place at E-days competition for our pipe/electronic organ. I conceived and led the project. I taught myself Verilog and programmed the FPGA and wrote a paper on a new method for synthesizing organ sounds.\\[.2cm]
\years{2007}\textbf{B.M., Piano Performance}\\
\emph{Colorado State University, 3.3 GPA.} Wendel Diebel award for musicianship. Also learned quite a bit of organ.

\end{document}
